\sectionTitle{Further Academic Service}{}

\begin{projects}

\projecta
	{Green RSE Special Interest Group (SIG) \lbrack\href{https://socrse.github.io/green-sig/committee.html#sadie-bartholomew}{\small{\websiteSymbol}}\rbrack}{Nov. 2024 - Present}
	{
	    \textit{Steering Committee Member and Lead on Governance}
	}
	{
    \begin{itemize}
        \item Member of a newly spun-up \href{https://socrse.github.io/green-sig/}{SIG} of volunteer research software engineers and researchers aiming to understand how to reduce the environmental impact of research software, leading on one of the seven 'GREENER' principles, Governance.
    \end{itemize}}

\projecta
	{RSEConUK'24 `Finding the Weather and Climate RSE Community' session \lbrack\href{https://society-rse.org/weather-and-climate-rsecon24-birds-of-a-feather-session-retrospective-blog-post/}{\small{\websiteSymbol}}\rbrack}{Sept. 2024}
	{
	    \textit{Panel member (by invitation)}
	}
	{
    \begin{itemize}
        \item Joined a panel of five invited speakers within the Birds of a Feather session to discuss audience-submitted questions related to the theme of research software engineering for/within the field of weather and climate research.
    \end{itemize}}

\projecta
	{CF Workshops 2023 and 2025 \lbrack\href{https://cfconventions.org/Meetings/2023-Workshop.html}{\small{\websiteSymbol}}\rbrack}{Throughout 2023, 2025}
	{
	    \textit{Co-organiser}
	}
	{\begin{itemize}
     \item On the organising committee for the annual international CF Workshop  held autumn 2023 and (due) 2025.
     \end{itemize}}

\projecta
	{Institute of Computing for Climate Science (ICCS) Summer School '23 \lbrack\href{https://iccs.cam.ac.uk/events/iccs-summer-school-2023}{\small{\websiteSymbol}}\rbrack}{July 2023}
	{
	    \textit{Panel member (by invitation)}
	}
	{
    \begin{itemize}
        \item Joined four other invited panel members for a panel discussion on `The Importance of Software Engineering Good Practices in Climate Science' at the 2023 ICCS Summer School.
    \end{itemize}}


\projecta
	{SIAM CSE '23, `Advances in High Performance Computing for Earth Science' session \lbrack\href{https://meetings.siam.org/sess/dsp_programsess.cfm?SESSIONCODE=75467}{\small{\websiteSymbol}}\rbrack}{Early 2023}
	{
	    \textit{Co-convener}
	}
	{\begin{itemize}
     \item Co-convener of the hybrid session `MS354 Advances in High Performance Computing for Earth Science - Part I of II' at the SIAM (Society for Industrial and Applied Mathematics) \href{https://www.siam.org/conferences-events/past-event-archive/cse23/}{Conference on Computational Science and Engineering}, including introducing parts of the session in-person in Amsterdam in March 2023.
     \end{itemize}
     }

\projecta
	{RSEConUK'22 `Coding Confessions' session \lbrack\href{https://www.youtube.com/watch?v=0BGYOYj7OjQ}{\small{\videoSymbol}}\rbrack}{Sept. 2022}
	{
	    \textit{Panel member}
	}
	{
    \begin{itemize}
        \item Joined a panel (with six other panel members) discussing common mistakes made in software.
    \end{itemize}}

\projecta
	{ExCALIBUR research programme ExCALIData project \lbrack\href{https://excalibur.ac.uk/}{\small{\websiteSymbol}}\rbrack}{Mid. 2022 - Present}
	{
	    \textit{Knowledge Exchange Coordinator}
	}
	{\begin{itemize}
     \item Took over from a colleague to act as ExCALIBUR Knowledge Exchange Coordinator for the \href{https://excalibur.ac.uk/projects/excalidata/}{`ExCALIData'} project, attending meetings on behalf of the project team to coordinate and collaborate with others across the wider programme.
     \end{itemize}}

\projecta
	{AGU Fall Meeting '21, `Accelerating Earth System Predictability: Advances in High-Performance Computing, Numerical Modeling, Artificial Intelligence, and Machine Learning' session}{Late 2021}
	{
	    \textit{Co-convener and chair}
	}
	{\begin{itemize}
     \item In virtual capacity, co-convener of the \href{https://agu.confex.com/agu/fm21/meetingapp.cgi/Session/152558}{`III eLightning (IN11C)'} component and chair of the \href{https://agu.confex.com/agu/fm21/meetingapp.cgi/Session/132759}{`II Oral (IN22A)'} and \href{https://agu.confex.com/agu/fm21/meetingapp.cgi/Session/129326}{`IV Poster (IN15C)'} components of the four-component session `Accelerating Earth System Predictability: Advances in High-Performance Computing, Numerical Modeling, Artificial Intelligence, and Machine Learning' at the AGU (American Geophysical Union) Fall Meeting held in December 2021.
     \end{itemize}}

\projecta
	{SeptembRSE, Walkthroughs and Workshops Team \lbrack\href{https://septembrse.society-rse.org/committee/}{\small{\websiteSymbol}}\rbrack}{Mid. 2021}
	{
	    \textit{Co-organiser}
	}
	{\begin{itemize}
     \item On the conference organising committee, specifically the `Walkthroughs and Workshops Team' for \href{https://septembrse.society-rse.org/}{SeptembRSE, the Fifth Conference of Research Software Engineers} (fully virtual due to the COVID-19 pandemic).
     \end{itemize}}

\end{projects}
% Manual page break has to be done here
\begin{projects}

\projecta
	{CF Conventions `Information Management and Support Team' member \lbrack\href{https://cfconventions.org/governance.html}{\small{\websiteSymbol}}\rbrack}{Jan. 2021 - Present}
	{
	    \textit{(Active) team member}
	}
	{\begin{itemize}
     \item Member, by initial invitation, of the formal team responsible for ``maintaining the [CF] conventions, enabling discussions and decisions, communication and record-keeping", for example by helping to incorporate continuous integration into the publication workflow and automate aspects of the standard name proposal workflow, plus improving the website.
     \end{itemize}}

\projecta
	{Performance optimisation of June, a COVID-19 epidemiology model
    \lbrack\href{https://github.com/IDAS-Durham/JUNE}{\small{\githubSymbol}}\rbrack}{Autumn 2020}
	{
	    \textit{Team member}
	}
	{\begin{itemize}
     \item Part of a small team from NCAS-CMS who worked with a team from Durham University Physics Dept. and the NHS to develop and optimise a new COVID-19 epidemiology model.
     \item We produced an $\mathcal{O}$(100) latency speedup to the pre-alpha stage, receiving formal acknowledgement in the \href{https://royalsocietypublishing.org/doi/10.1098/rsos.210506}{release paper}.
     \end{itemize}}

\projecta
	{Journal of Open Source Software \lbrack\href{https://joss.theoj.org/}{\small{\websiteSymbol}}\rbrack}{June 2020 - Present}
	{
	    \textit{Reviewer}
	}
	{\begin{itemize}
     \item Formal review in traditional two reviewer process for a number of papers seen through to publication, such as:
     \begin{itemize}
        \item 'IPART: A Python Package for Image-Processing based Atmospheric River Tracking' \lbrack\href{https://joss.theoj.org/papers/10.21105/joss.02407}{\small{\websiteSymbol}}\rbrack
        \item 'OpenSCM Two Layer Model: A Python implementation of the two-layer climate model'
        \lbrack\href{https://joss.theoj.org/papers/10.21105/joss.02766}{\small{\websiteSymbol}}\rbrack
        \item 'qgs: A flexible Python framework of reduced-order multiscale climate models'
        \lbrack\href{https://joss.theoj.org/papers/10.21105/joss.02597}{\small{\websiteSymbol}}\rbrack
    \end{itemize}
     \end{itemize}}

%\projecta
%	{TODO}{TODO - Present}
%	{
%	    \textit{TODO}
%	}
%	{\%begin{itemize}
    % \item TODO
     %\item TODO
%     \%end{itemize}}

\end{projects}
\vspace{-3mm}