\sectionTitle{Engagement and Outreach}{}
\begin{talks}

\projecta
	{`Science in Parallel' podcast episode `Sadie Bartholomew: Patterns in Computing and Art' [\href{https://scienceinparallel.org/2024/11/sadie-bartholomew-patterns-in-computing-and-art/}{\small{\websiteSymbol}}]}{\hspace*{16cm} Nov. 2024}
	{
	    \textit{Invited feature guest}
	}
	{\begin{itemize}
     \item Invited to be the individual subject of an episode for `Science in Parallel', a USA-based podcast ``about people and projects in computational science" due to interest in work due to be displayed for the `Art of HPC Display' at SC24 (see item below). Interviewed remotely in Sept. 2024 with the episode broadcast to coincide with SC24.
     \end{itemize}}

\projecta
	{`Art of HPC Display', The International Conference for High Performance Computing, Networking 2024 (SC24) ~ [\href{https://sc24.conference-program.com/session/?sess=sess553}{\small{\websiteSymbol}}]}{Nov. 2024}
	{
	    \textit{Exhibitor}
	}
	{\begin{itemize}
     \item Four entries of creative coding designs selected for inclusion and exhibited at the `Art of HPC Display' poster session at SC24: \href{https://sc24.supercomputing.org/proceedings/art_of_hpc/art_of_hpc_pages/art115.html}{`Collatz Kaleidoscope'}, \href{https://sc24.supercomputing.org/proceedings/art_of_hpc/art_of_hpc_pages/art117.html}{`Collatz Residuals'}, \href{https://sc24.supercomputing.org/proceedings/art_of_hpc/art_of_hpc_pages/art131.html}{`Connections in Rotation'}, \href{https://sc24.supercomputing.org/proceedings/art_of_hpc/art_of_hpc_pages/art132.html}{`Undulations in Rotation'}.
     \end{itemize}}

\projecta
	{Society of Research Software Engineering Blog, `Weather and Climate RSECon24 Birds of a Feather Session
Retrospective Blog Post' ~ [\href{https://society-rse.org/weather-and-climate-rsecon24-birds-of-a-feather-session-retrospective-blog-post/}{\small{\websiteSymbol}}]}{Oct. 2024}
	{
	    \textit{Co-author}
	}
	{
    \begin{itemize}
     \item Co-produced a reflection upon the weather and climate research software engineering interest \href{https://docs.google.com/presentation/d/1EroCJEARScMQy9Sjqnuubzx4VeOEazJ9U4f8JuYnByo/edit#slide=id.p}{session held at RSECon24}.
     \end{itemize}
     }

\projecta
	{SSI Blog Post `Tracking the environmental impact of research computing' ~ [\href{https://www.software.ac.uk/blog/tracking-environmental-impact-research-computing}{\small{\websiteSymbol}}]}{Aug. 2023}
	{
	    \textit{Co-author}
	}
	{\begin{itemize}
     \item Co-produced an article to educate on, and advocate for, greener research computing practice.
     \end{itemize}}

\projecta
	{`Code for Thought' podcast episode `Green Computing at the RSE Conference 2024 in Newcastle' ~ [\href{https://codeforthought.buzzsprout.com/1326658/episodes/15766448-en-bonus-green-computing-at-the-rse-conference-2024-in-newcastle}{\small{\websiteSymbol}}]}{\hspace*{16cm} May 2023}
	{
	    \textit{Invited guest}
	}
	{\begin{itemize}
     \item Represented the CATS team, alongside one other team member, invited to speak on the `Code for Thought' podcast episode focusing on green computing (see `Chapters' \rightarrow \hspace{1mm} `26:29, Sadie Bartholomew \& Colin Sauzé').
     \end{itemize}}

\projecta
	{`The Turing Way' handbook chapter `Environmental Impact of Digital Research' [\href{https://book.the-turing-way.org/ethical-research/activism/activism-env-impact.html}{\small{\websiteSymbol}}]
  }{Summer 2023}
	{
	    \textit{Contributor}
	}
	{\begin{itemize}
     \item Contributed to \href{https://book.the-turing-way.org/}{`The Turing Way'}, a ``handbook to reproducible, ethical and collaborative data science", notably co-writing, co-reviewing and overseeing to publication a new chapter `Environmental Impact of Digital Research'.
     \end{itemize}}

\projecta
	{Meteorology Dept. Research Blog Post, `What’s that data? Why and how the geoscientific community is forging metadata standards' ~ [\href{https://blogs.reading.ac.uk/weather-and-climate-at-reading/2021/whats-that-data-why-and-how-the-geoscientific-community-is-forging-metadata-standards/}{\small{\websiteSymbol}}]}{Jan. 2021}
	{
	    \textit{Author}
	}
	{\begin{itemize}
     \item Advocated for the importance of metadata standards to the department and wider weather and climate community. 
     \end{itemize}}

\end{talks}    
\vspace{-3mm}
