\sectionTitle{Supervision, Training and Teaching Roles}{}

\begin{projects}

\projecta
	{Research Placements and Experiences}{July - Sept. 2024}
	{
	    \textit{Supervisor to two students}
	}
	{\begin{itemize}
     \item Individually supervised, hosting in-office, two local school Year 12 students each on two-week placements as part of the `Research Placements and Experiences' (formerly `Nuffield Research Placements') scheme, to contribute towards the \href{https://ncas.ac.uk/for-staff/change/}{NCAS `Community for Change' initiative}.
     \item As an outcome five new code recipes, designed by the students, will be added to the cf-python documentation.
     \end{itemize}}

\projecta
	{NCAS `Introduction to Scientific Computing' training course ~ [\href{https://ncas.ac.uk/study-with-us/introduction-to-scientific-computing/}{\small{\websiteSymbol}}] [\href{https://github.com/ncasuk/ncas-isc}{\small{\githubSymbol}}]}{Early 2024 - Present}
	{
	    \textit{Co-organiser and co-delivery}
	}
	{\begin{itemize}
     \item Helped, and doing so going forward, to organise, create content for, and co-deliver in-person the NCAS `Introduction to Scientific Computing' atmospheric science focused training course (held roughly annually) starting from the one held over a week in Nov. 2024. Working to synergise this with the NCAS `Data Analysis Tools’ training (see below).
     \end{itemize}}
     
\projecta
	{NCAS Early Career Symposium ~ [\href{https://sites.google.com/ncas.ac.uk/ncasharmonyintheskies/home}{\small{\websiteSymbol}}]}{Jan. 2024 - Present}
	{
	    \textit{Co-organiser and co-delivery}
	}
	{\begin{itemize}
     \item Helped, and doing so going forward, to organise and deliver the annual NCAS Early Career Symposium, beginning with the inaugral event `Harmony in the Skies: Bridging Horizons in Atmospheric Science' held in March 2024.
     \item Contribution included \href{https://github.com/sadielbartholomew/sadielbartholomew/blob/master/talks-and-workshops/ncas-ec-symposium-software-data.pdf}{co-producing content and co-presenting on} software and data standards.
     \end{itemize}}

\end{projects}
% Manual page break has to be done here
\begin{projects}

\projecta
	{CF Conventions Training ~ [\href{https://cfconventions.org/Training/}{\small{\websiteSymbol}}]}{Summer 2022 - Present}
	{
	    \textit{Co-founder, co-organiser and co-delivery} ~ 
	}
	{\begin{itemize}
     \item Co-founded the CF Training Committee to instigate, organise and advertise new training dedicated to the CF Conventions for researchers, RSEs and data managers etc. Towards this, co-organised and produced materials for the first ever \href{https://cfconventions.org/Training/2022-Training-Workshop.html}{CF Training Workshop} held in Sept. 2022 and presented on the training (e.g. see \textbf{AGU’23C}) to encourage new engagement.
     \end{itemize}}

\projecta
	{The Carpentries ~ [\href{https://github.com/sadielbartholomew/sadielbartholomew/blob/master/assets/carpentries_instructor_certificate.pdf}{\small{\faCertificate}}]}{Summer 2022}
	{
	    \textit{Certified Instructor}
	}
	{\begin{itemize}
     \item Took the dedicated training and test to qualify as a \href{https://carpentries.org/instructors/}{Certified Instructor} for \href{}{The (Software, Data \& Libraries) Carpentries}, an international group with the aim to ``teach foundational coding and data science skills to researchers worldwide".
     \end{itemize}
     }

\projecta
	{Learning to Code Programme ~ [\href{https://www.software.ac.uk/mentorship-programme/mentorship-programme-2021}{\small{\websiteSymbol}}]}{Autumn 2021}
	{
	    \textit{Formal mentor to one graduate student}
	}
	{\begin{itemize}
     \item Individually mentored (remotely) in Python a psychology graduate in 2021 as part of the Software Sustainability Institute's `Learning to Code' mentorship programme for her project entitled `Manipulation of data stored in spreadsheets using Python tools' (see \href{https://www.software.ac.uk/blog/learning-code-my-experience-psychology-graduate}{her blog post} summarising the project).
     \end{itemize}}

\projecta
	{NCAS `Data Analysis Tools' training course ~ [\href{https://ncas.ac.uk/study-with-us/data-analysis-tools/}{\small{\websiteSymbol}}] [\href{https://github.com/NCAS-CMS/cf-tools-training}{\small{\githubSymbol}}]}{Feb. 2020 - Present}
	{
	    \textit{Co-organiser and co-delivery}
	}
	{\begin{itemize}
     \item Jointly organising and delivering the NCAS `Data Analysis Tools' training course, last held in person in March 2020 (then postponed due to the COVID-19 pandemic). We have since updated the course materials and aim to start running the course more regularly again, starting summer 2025.
     \end{itemize}}

% BACKUP ONLY
%\projecta
%	{TODO ~ [\href{TODO}{\small{\websiteSymbol}}] [\href{TODOLINK}{\small{\githubSymbol}}]}{TODODATES}
%	{
%	    \textit{TODOROLE} ~ 
%	}
%	{\begin{itemize}
%     \item TODO 
%     \item TODO
%     \end{itemize}}


\end{projects}
\vspace{-3mm}
